Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd

>>>>

### Google Survey Link
https://forms.gle/81vCBvH8t7B9NfJ69

### Google Survey 
**U.S. Presidential Election Survey 2024**

-This survey is part of a research study aimed at forecasting the 2024 U.S. Presidential Election. Your responses are confidential and will be used solely for research purposes. This survey will take approximately 5 minutes to complete.

**Are you eligible to vote in the 2024 U.S. Presidential Election?**

-Yes
-No

**Are you planning to vote in the upcoming 2024 U.S. Presidential Election?**

-Yes
-No
-Maybe

**What is your current party affiliation?**
-Democratic Party
-Republican Party
-Independent
-Other (please specify)
-Prefer not to say

**Did you vote in the 2020 U.S. Presidential Election?**
-Yes
-No
-Prefer not to say

**If the presidential election were held today, which candidate would you most likely vote for?**
-Kamala Harris (Democratic Party)
-Donald Trump (Republican Party)
-Another candidate (please specify)
-Undecided
-Prefer not to say

**How likely are you to vote in the 2024 U.S. Presidential Election?**

Least likely | 1 | 2 | 3 | 4 | 5 | Most likely

**What is your age?**

**What is your gender?**
-Male
-Female
-Non-binary/Third gender
-Prefer not to say

**What is your race/ethnicity?**
-White
-Black or African American
-Hispanic or Latino
-Asian
-Native American or Alaska Native
-Native Hawaiian or Pacific Islander
-Prefer not to say
-Other (please specify)

**What is your highest level of education?**
-Less than high school
-High school graduate
-Some college
-Bachelor’s degree
-Postgraduate degree
-Prefer not to say

**What is your approximate annual household income?**
-Less than 25,000
-25,000 to 49,999
-50,000 to 74,999
-75,000 to 99,999
-100,000 or more
-Prefer not to say

**To ensure the quality of our data, please select "Blue" from the options below:**

- Red
- Blue
- Green
- Yellow

---

**Conclusion**

Thank you for your participation!  
Your responses have been recorded.
